\newpage
\appendix
\section{2D SOMs of subsets}

        In Fig.~\ref{fig: subset2}, which is the SOM results from data listed in Table~\ref{tab: subset2}, distance between positions of the region 7, and region 3 is much larger compare to the one in Fig.~\ref{fig: all_derived_ones}. 
        IRAC 5.7~$\mu$m flux in the region 7 and the region 3 is similar to each other. 
        Therefore, removing flux from IRAC 5.7 $\mu$m removed the one source of similarity in these two regions and they moved further from each other in the SOM.
        The positions of the regions 2 and 9 are closer to each other, but the weight distance between them is much higher (the colours between them are became almost black). 
        In general by removing IRAC 5.7 $\mu$m  flux data from the input data, the colours between regions become much more darker.
        \import{../sections/tables/}{subset2.tex}
        \import{../sections/image_texts/}{subset2.tex}
        
        In Fig.~\ref{fig: subset3}, the positions from the region 9 is much closer to the positions of the regions 4 and 7. 
        Since region 4 and 5 have a similar [~\oiii] and [~\sii] continuum fluxes, by removing these two values from the input data distance between regions 4 and 5 became much smaller.
        The positions of the regions 2 and 6 are closer together, but the colours between their neurons are darker.
        The wining neurons for regions 1 and 9 are moved further from each other, but the colours between them are slightly lighter. 
        moreover, similar to regions 4 and 5, [~\oiii] and [~\sii] continuum fluxes for regions 1 and 9, and regions 8 and 6 are similar to each other, and removing these two values from input data, reduces the similarity between these regions. Therefore, they moved further from each other. 
        \import{../sections/tables/}{subset3.tex}
        \import{../sections/image_texts/}{subset3.tex}
        
        In the results from the subset 4 in Fig.~\ref{fig: subset4}, regions 8 and 6 moved closer to each other. 
        These two regions have distinct metallicity, removing metallicity from input data caused these two stay in a closer neurons. 
        Since regions 1 and 2 have similar metallicity and total PAHs, and their total stellar mass are comparable, removing these values from input data made the position of the regions 1 and 2 moved further from each other. 
        \import{../sections/tables/}{subset4.tex}
        \import{../sections/image_texts/}{subset4.tex}
        
        The positions of the region 8 and 5 are moved closer in Fig.~\ref{fig: subset7}.
        Both of these regions are around the inner ring inside the galaxy.
        Therefore, both of them have similar values in most of the input parameters.
        However, they have very different fluxes in IRAC 5.7 $\mu$m and [~\sii] continuum, which removing these two fluxes from the input data moved their position on the SOM closer.
        TIR luminosity and IRAC 5.7 $\mu$m flux for regions 3 and 5 are different, and removing them from the input data caused the distance between their position decreases. 
        In Fig.~\ref{fig: subset7} the relations between all the other regions are mostly unchanged.
        \import{../sections/tables/}{subset7.tex}
        \import{../sections/image_texts/}{subset7.tex}
        